\vspace{-2.5cm}A generative model for urban firm networks

### 2020-09-16 communications/NetSci2020/slidesNetSci.tex
fix_compil

\sframe{Simulation of urban networks}

{
    % examples

    \begin{center}
    \includegraphics[width=0.48\textwidth]{figuresraw/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{figuresraw/ex_alleq-lowgravity_seed-12102_t1500.png}
	\end{center}

@@

    \includegraphics[width=0.48\textwidth]{figuresraw/internationalisation-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figuresraw/rhoDegreeSize-gravityDecay_errorbars.png}

@@

     \includegraphics[width=0.48\textwidth]{figuresraw/internationalisation-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{figuresraw/rhoDegreeSize-gammaSectors_errorbars.png}

@@

    \begin{center}
    \includegraphics[width=\textwidth]{figuresraw/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

@@

    \begin{center}
    	\includegraphics[height=0.6\textheight]{figuresraw/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}

>>>>

\sframe{Simulation of urban networks}{
    % examples

    \begin{center}
    \includegraphics[width=0.48\textwidth]{../../figuresraw/ex_alleq-highgravity_seed-12102_t1500.png}\hspace{0.1cm}
    \includegraphics[width=0.48\textwidth]{../../figuresraw/ex_alleq-lowgravity_seed-12102_t1500.png}
	\end{center}

@@

    \includegraphics[width=0.48\textwidth]{../../figuresraw/internationalisation-gravityDecay_errorbars.png}
    \includegraphics[width=0.48\textwidth]{../../figuresraw/metropolisation-gravityDecay_errorbars.png}

@@

     \includegraphics[width=0.48\textwidth]{../../figuresraw/internationalisation-gammaSectors_errorbars.png}
    \includegraphics[width=0.48\textwidth]{../../figuresraw/metropolisation-gammaSectors_errorbars.png}

@@

    \begin{center}
    \includegraphics[width=\textwidth]{../../figuresraw/internationalization_countryGravityDecay200_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
    \end{center}

@@

    \begin{center}
    	\includegraphics[height=0.6\textheight]{../../figuresraw/networkAvgCommunitySize_countryGravityDecay2100_gammaDestination0_facetwrapgammaOrigin_colorgammaSectors.png}
